{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-11-06 documents/supplemental.tex
TCL dump

>>>>

For in-vitro research, it seems to me that perhaps this field is running into the issues Feynman's rat-races \cite{Cargo}. There are a large number of very tricky variables. Requires analysis fo the very details of how the study was conducted, rather than simply its results. While the measurements

Of course, we commit the very same mistakes and fall into the same traps, we are not immune from criticism.

In some cases, these are thoroughly characterized and described. UWB rat paper.

But it seems to me that each worker (myself included!) is using their own test arrangement; and yet the studies are not so different as to require such customization.

It occurs to me that perhaps a set of exquisitely characterized standardized test cells and procedures would be helpful; and a requirement that any papers on the topic either use such a cell, or if their study requires some exceptional treatment, to follow an established procedure to add a new cell to the standard.

Alternatively, methods such as the optical hetrodyne one,

If possible, very specific buffer compositions should be made universal.

What heating patterns can be expected from a certain microwave input? What modes can be introduced by deviations in machining tolerances?

Then, of course, are the questions of the excitation: what brand of attenuators are satisfactory?

Of course, one cell could not suffice for the whole range of microwave frequencies.

There is also the matter that the scientific publishing infrastructure could perhaps provide for a "scientific lineage". We often hear of a "scientific record": journals will retract a paper from "the record"; but where {\it is} this record? Where is the chain of trust upon which new results can be added? Each paper is forced to supply its own context; each worker is forced to re-dredge the entire chain of truth, to discover the controversy which clouds some papers; each offers its own interpretation of the literature. It is inevitable that some history will be lost; that the wrong starting point will be taken up; a veritable fork in the literature. Especially as the volume of scientific research increases as society proceeds. The only data is a few references per paper, and a date for each! Another such record exists in comprehensive books written by workers on the topic.

But is this not an artifact of the limitations of printed journals, whereby papers must necessarily be individual entities? Is there no way by which papers can be arranged so that they each supply a visible part of the jigsaw, where each paper brings with it the complete story of the field?

Scite.ai and similar services, but it feels like these are tacked-on workarounds to re-add metadata which should have existed in the first place.

Consider the non-thermal effects literature. It starts, perhaps, in the 1800s;
